\documentclass[../main.tex]{subfiles}

\begin{document}

\subsection{Purpose}

\epigraph{The new model is mobile pervasive computing, and it will change the very nature of the enterprise}{\textit{Carl Yankowski - Former CEO, Palm, Inc.}}
%TODO - needs revision
%We are designing Data4Help, a software system capable of sending and receiving informations about our customers, collected trough the use of wearable devices, as accurately as the currently widely available technology permits.
%Such information includes current location, in terms of geographical position, and body parameters, such as heartbeat rate and blood pressure.

%We believe this data has great value, so we'll make it available for other companies to use for their purposes; they will only need to file a request to our system that, when approved, will guarantee access to our information, currently collected and yet to be, regarding a specific customer or to a group of people satisfying certain criteria.

%Moreover, we will offer two other services that will make use of this data base.

%The first one is AutomatedSOS, that will target mainly elderly people. Our software will constantly monitor their health status, and in case of emergency will promptly dispatch an ambulance to their current location, notifying the customer of its arrival.

%The second one is Track4Run, which will allow the organizers of a running event to define the path for it, the athletes to enroll in the event, and the spectators to track the position of the runners on a map in real time.

In the last few years wearable devices are increasingly used. The evolution of wearables in the medical field has made possible to measure vital parameters useful for understanding the state of health of a person. The application for TrackMe uses this feature.

The main service is Data4Help which is a software system capable of sending and receiving informations about our customers, collected through the use of wearable devices, as accurately as the currently widely available technology permits. Such information includes current location, in terms of geographical position, and body parameters, such as heartbeat rate and blood pressure. 
This data has great value so the goal is to make it available for other companies to use for their purposes; they will only need to file a request to the system that, when approved, will guarantee access to information, currently collected and yet to be, regarding a specific customer or to a group of people satisfying certain criteria. 

Moreover, the software will offer two other services that will make use of this data base. 

The first one is AutomatedSOS, which will target mainly elderly people. The software will constantly monitor their health status, and in case of emergency will promptly dispatch an ambulance to their current location, notifying the customer of its arrival. 

The second one is Track4Run, which will allow the organizers of a running event to define the path for it, the athletes to enroll in the event, and the spectators to track the position of the runners on a map in real time.

\subsubsection{Goals}

\begin{minipage}{\textwidth}
{\bf Data4Help}
\begin{description}
	\item [G1]  Third parties shall be able to make requests for accessing single customer data.
	\item [G2]  Third parties shall be able to make requests for accessing aggregate anonymous data specifiying filters.
	\item [G3]  Third parties shall be able to access stored data, for which a request has been approved.
	\item [G4]  Third parties shall be able to subscribe to new data, for which a request has been approved.
	\item [G5]  Users shall be able to accept or refuse requests for their data from third parties.
	\item [G6]  Access to customers data from a third party, for which a request does not exist, or has been rejected, shall be denied.
\end{description}
\end{minipage}
\vspace{8mm}

\begin{minipage}{\textwidth}
{\bf AutomatedSOS}
\begin{description}
	\item [G7]  From the time a customer's parameters indicate a health emergency status, an ambulance shall be dispatched to his location in less than 5 seconds.
	\item [G8]  When an ambulance is dispatched, the customer shall be notified of its arrival.
\end{description}
\end{minipage}
\vspace{8mm}

\begin{minipage}{\textwidth}
{\bf Track4Run}
\begin{description}
	\item [G9]   Organizers shall be able to create a new running event.
	\item [G10]  Runners shall be able to view and enroll in available runs.
	\item [G11]  Spectators shall be able to see the position of participants on the map during a run.
\end{description}
\end{minipage}

\subsection{Scope}

The main purpose of Data4Help is creating a bridge between companies and individuals health status and location. As such, the main beneficiaries will be companies such as life insurances, hospitals and clinics, and universities for research purposes.
The focus of our two other services, AutomatedSOS and Track4Run, is instead on the single customer, mainly elderly people and runners respectively.

The software will collect customer's data through wearable devices; they'll need to either have GPS and an active internet connection per se, or a paired smartphone through which the customer will be localized and data will be sent and received via internet. We'll target Wear OS and Android as running platform. Companies on the other hand will be able to access our stored data through a REST web API.

% TrackMe is an application that will be used by two types of users:
%
% -Third party users who are interested to people’s data for some reason (e.g. Statistics).
%
% -Individual users that decide to give their information to the application and after positive answer to requests give it to third party users.
%
% The function “Data4Help” cover these scopes.
%
% With AutomatedSOS feature TrackMe also becomes useful for those people who want their vital parameters to be constantly monitored. In this way in case of emergency they can be assisted immediately thanks to an automatic call to the ambulance.
%
% The last feature is called “Track4Run”, it allows users to organize running competition or to enroll to them. The users can also localize all participant of a running competition.
% The data will be collected through a wearable device like a smartwatch and will send to personal smartphone where the application installed (Android or iOS) or the web app organize data and save it in a server to be used. The notification of requests will be sent to user’s smartphone.

\subsection{Definitions, acronyms, abbreviations}

\subsubsection{Definitions}
\begin{description}

	\item [Third party company] A company that wants to use our services.
	\item [Wearable (device)] Electronic device meant to be worn on human body.
	\item [Backend] The part of a program that carries out the tasks the program is designed to perform as opposed to the front end of the program that allows the user to instruct and interact with the back end.
	
\end{description}


\subsubsection{Acronyms}
\begin{description}

	\item [RASD] Requirement Analysis and Specification Document.
	\item [API] Application Programming Interface.
	\item [SSN] Social Security Number.
	\item [FC] Fiscal Code, SSN used in Italy.
	\item [UI] user interface.
	\item [UX] user experience.
	\item [RAID] Redundant Array of Independent Disks, data storage virtualization technology that combines multiple physical disk drive components into one or more logical units.
	\item [MTTR] Mean Time To Failure, the length of time a device or other product is expected to last in operation

\end{description}

\subsubsection{Abbreviations}
\begin{description}

	\item [Third party] Third party company.
	\item [Company] Third party company.

\end{description}

\subsection{Revision history}

%\begin{center}
	\begin{tabular}{p{1.2cm}|p{2.1cm}|p{2.6cm}}
		\bf Version & \bf \makebox[2.1cm][c]{Release Date} & \bf \makebox[3cm][c]{Description} \\
		\hline
		\makebox[1.2cm][c]{1.0} & \makebox[2.1cm][c]{11/10/2017} & \makebox[3cm][c]{Initial Release}\\
	\end{tabular}
%\end{center}

\subsection{Referenced documents}

\begin{minipage}{\textwidth}
\begin{description}
	\item [BEEP channel] - Mandatory Project Assignment
	\item [The world \& the machine] - M. Jackson, P. Zave
	\item [developers.google.com] - Google Fit API overview (https://developers.google.com/fit/overview)
	\item [developer.apple.com] - watchOS API overview (https://developer.apple.com/documentation/watchkit)
	\item [statista.com] - Smartwatch market share of overall wearable market worldwide in 2018 and 2022, by operating system (https://www.statista.com/statistics/750328/worldwide-smartwatch-market-share-by-platform/)
	\item [statista.com] - Preferred time of the day to run worldwide (https://www.statista.com/statistics/933781/united-states-preferred-time-of-day-to-run-as-a-sport/)
	\item [statista.com] - Android versions distribution (https://www.statista.com/chart/10761/adoption-of-latest-android-versions/)
\end{description}
\end{minipage}

\subsection{Document structure}

This document is structured in four main chapters, that are as follows:

\begin{enumerate}
	\item The first chapter serves as an introduction and an overview to the project, describing the main reasons for its development, what are its goals and giving a brief informat description of it.

	\item The second chapter serves as a more formal description of the project: it includes class diagrams, state machine diagrams, and it gives details on the shared phenomena and domain models. Class diagrams give a big picture description on how the system should be structured, while state machine diagrams focus on the more relevant entities of the model. Here are also presented all the requirements and domain assumptions the system in project must fulfill and take into considerations, in order to achieve the goals; they are presented each one after the goal it is relevant to.

	\item In the third chapter are presented the specific requirements, use cases described through the use of natural language and diagrams such as sequence/activity diagram, and the design constraints the system must satisfy. A mockup is also shown as a general idea of how the end product should be, in terms of design and functionalities offered to the end user.

	\item The fourth and last chapter is a formal analysis of the model, made through the use of the open source Alloy language and analyzer, including a graphic representation of it obtained from Alloy Tool.
\end{enumerate}

\end{document}
