\documentclass[../main.tex]{subfiles}

\begin{document}

\subsection{Purpose}

This document provides a specification on the architecture of TrackMe's system. It is complementary to the Requirements Analysis and Specification Document already presented, and it provides further description on its components, their interactions, and the implementation, integration and testing plan.

\subsection{Scope}

The document will focus on illustrating the following components of the application and its development process:

\begin{itemize}

	\item{System architecture}
	\item{UX}
	\item{Implementation, integration and testing plan}

\end{itemize}

\subsection{Definitions, Acronyms, Abbreviations}


	\subsubsection{Definitions}
		\begin{description}
			\item[Gated Commit] a software integration pattern that reduces the chances for breaking a build (and often its associated tests) by committing changes into the main branch of version control.
			\item[Verigreen] Verigreen is a lightweight, server side solution for verification of git commits. It is a gated check-in process which will not allow any failed CI commit to go into an integration/release/any protected branch.
			\item[Jenkins]  Jenkins is an open source automation server written in Java. Jenkins helps to automate the non-human part of the software development process, with continuous integration and facilitating technical aspects of continuous delivery
		\end{description}

	\subsubsection{Acronyms}
		\begin{description}
			\item[UX] User experience
			\item [RASD] Requirements Analysis and Specification Document
			\item [CIA triad] Confidentiality, Integrity, Availability; a model designed to guide policies for information security within an organization
			\item [API] Application Programming Interface
			\item [CI] Continous Integration
		    \item [CRUD] Create, Read, Update, Delete; basic functions of persistent storage, also translates to proper HTTP verbs
			\item [REST] Representational State Transfer
		\end{description}

\subsection{Revision history}
% \begin{tabular}{p{1.2cm}|p{2.1cm}|p{2.6cm}}
% 	\bf Version & \bf \makebox[2.1cm][c]{Release Date} & \bf \makebox[3cm][c]{Description} \\
% 	\hline
% 	\makebox[1.2cm][c]{1.0} & \makebox[2.1cm][c]{10/12/2018} & \makebox[3cm][c]{Initial Release}\\
% \end{tabular}

\begin{description}
	\item [v. 1.0 - 10/12/2018] Initial release
	\item [v. 1.1 - 13/01/2019] Removed unnecessary Data Access Manager component; added Database Server subcomponents; adjusted sequence diagrams on fig. 10 and 11.
\end{description}

\subsection{Reference Documents}

\begin{itemize}

	\item{Mandatory Project Assignment AY 2018/2019}

\end{itemize}

\subsection{Document Structure}

The structure of this document is the following:

\begin{enumerate}

	\item The first chapter serves as an introduction to this document.
	\item The second chapters details the architecture of TrackMe's system: its components, the way they interact with each other, and how are grouped together. It also comprises sequence diagrams that show in more detail the interactions of such components for some selected goal to be achieved. Futhermore, and the end of this chapter, can be found the architectural and design patterns that are used in the system, their purpose and the reason for choosing them, along with other design decisions.
	\item The third chapter futher describes the indications on the user interfaces and user experience provided in the RASD.
	\item In the fourth chapter is provided a map on which components of the system every requirement and goal specified in the RASD is achieved.
	\item The fifth chapter illustrates the plan for the implementation, integration and testing of the system to be developed.

\end{enumerate}

\end{document}
